Supplementary Information

### 2020-12-21 doc/manuscript/MEE_manuscript.Rmd
update results

### Identifying key climate drivers {-#Identifying}

@@

## Identifying climate drivers {-#Identifying}

@@

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Dec.21)
# BCI: precip dry season (12mo), T dry season (2 mo) 
#HKK: PDF dry season + edges (9mo), T wet season (8 mo)
#SCBI: precip p June - cAug (15 mo), PET current gs (3 mo)
#LDW: precip c June (1 mo), PET current June (1mo)
#HF: PDF pMay (1mo), PET cMar (1mo)
#ZOF: pre pJune-pJul (2mo), TMX Jan-Mar (3mo)
#NIO: wet cMay (1mo), TMP pJune (1mo)
#LT: pNov-cJul (9mo), TMX cMay-Jul (3mo)
#CB: cApr-cJul(4mo), TMXpJul-cJul(13mo)
#SC:pJun-pAug(3mo), TMXcJul (1mo)
```
Optimal time windows most commonly coincided at least partially with the months of most active growth in the current year (Fig. `r clim_sens`; Table `r site_details`): wet seasons in the tropics (precipitation variables at both BCI and HKK; $T_{max}$ at HKK) or late spring/ early summer in the extratropics (n= 5 of 8 each for temperature and precipitation variables).
In the tropics, the windows over which precipitation was influential included part (BCI) or all (HKK) of the dry season.
In the extratropics, there were two cases where temperature variables were most influential in late winter/early spring (March $PET$ at HF; Jan-March $T_{max}$ at ZOF; Fig. `r clim_sens`).
*(Results before this are up-to-date as of Dec. 21. The following need updating.)*
There were also cases where previous growing season conditions were influential:...
At the *5 lowest latitude* sites (BCI, HKK, LT, CB, and SCBI), the optimal window for precipitation variables spanned $\ge$ 8 months, ending during the peak growing months of the year of ring formation. 
At the *3 highest latitude sites* (HF, ZOF, and SC), the optimal window for precipitation variables was a short ($\le$ 3 months) window during the previous growing season.
Optimal windows for temperature variables tended to be shorter, the longest being a *6*-month period during the summer (wet season) at HKK. 
At two of the higher-latitude temperate sites (HF and Žofín), temperatures were most influential during late winter/ early spring.
There were also a few instances where previous growing season conditions had the strongest influence.

>>>>

### Climate variable selection {-#Climate}

@@

## Climate variable selection {-#Climate}

@@

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Dec.21)
# BCI: precip dry season (12mo), T dry season (2 mo) 
#HKK: PDF dry season + edges (9mo), T wet season (8 mo)
#SCBI: precip p June - cAug (15 mo), PET current gs (3 mo)
#LDW: precip c June (1 mo), PET current June (1mo)
#HF: PDF pMay (1mo), PET cMar (1mo)
#ZOF: pre pJune-pJul (2mo), TMX Jan-Mar (3mo)
#NIO: wet cMay (1mo), TMP pJune (1mo)
#LT: pNov-cJul (9mo), TMX cMay-Jul (3mo)
#CB: cApr-cJul(4mo), TMXpJul-cJul(13mo)
#SC:pJun-pAug(3mo), TMXcJul (1mo)
```
Optimal time windows most commonly coincided at least partially with the months of most active growth in the current year (Fig. `r clim_sens`; Table `r site_details`): wet seasons in the tropics (precipitation variables at both BCI and HKK; $T_{max}$ at HKK) or late spring/ early summer in the extratropics (n= 5 of 8 each for temperature and precipitation variables).
In the tropics, the windows over which precipitation was influential included part (BCI) or all (HKK) of the dry season.
In the extratropics, there were two cases where temperature variables were most influential in late winter/early spring (March $PET$ at HF; Jan-March $T_{max}$ at ZOF; Fig. `r clim_sens`).
There were also cases where previous growing season conditions were influential, including precipitation variables at SCBI, Harvard Forest, Zofin, and Scotty Creek, and temperature variables at Niobrara and Cedar Breaks. 
In two cases ($PPT$ at SCBI and $T_{max}$ at Cedar Breaks), the window of influence spanned >12 months to include past and current growing seasons.
